A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-01-16 ICLP Paper/samplepaper.tex
update tables

\begin{table}[ht]
	\fontsize{19pt}{30pt}
	\caption{Results for JSP $50 \times 15$ instances with different TWs} \label{tab: Table01}
	\centering
	%\resizebox{\columnwidth}{!}{%
	\rotatebox{90}{
	\begin{adjustbox}{width=1.7\textwidth}
	\begin{tabular}{|M{2.0cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|}

	%\begin{tabular}{l c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c}
		\hline
		\multirow{3}*{\textbf{{\large Instances}}}  &  \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 01}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 02}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 03}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 04}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 05}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 10}}}} \\[1cm]

		\hline
		& {\large Makespan} & {\Large Timeout}  & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} &  {\large Makespan} & {\Large Timeout} & {\large Interr-calls}\\[1cm]

		{\LARGE TA51} & $3594.0$ & $1000.0$ & $1.0$ & $\mathbf{3442.0}$ & $1000.0$ & $2.0$ & $3843.0$ & $1000.0$ & $3.0$ & $4049.0$ & $1000.0$ & $4.0$ & $3965.0$ & $994.5$ & $4.0$ & $4269.0$ & $287.7$ & $2.0$\\[1cm]

		{\LARGE TA52} & $3638.0$ & $1000.0$ & $1.0$ & $3750.0$ & $1000.0$ & $2.0$ & $\mathbf{3613.0}$ & $1000.0$ & $3.0$ & $3850.0$ & $1000.0$ & $4.0$ & $4022.0$ & $1000.0$ & $5.0$ & $4256.0$ & $241.1$ & $1.0$\\[1cm]

		{\LARGE TA53} & $\mathbf{3388.0}$ & $1000.0$ & $1.0$ & $3497.0$ & $1000.0$ & $2.0$ & $3566.0$ & $1000.0$ & $3.0$ & $3618.0$ & $1000.0$ & $4.0$ & $3803.0$ & $1000.0$ & $5.0$ & $4065.0$ & $206.6$ & $2.0$\\[1cm]

		{\LARGE TA54} & $3434.0$ & $1000.0$ & $1.0$ & $3489.0$ & $1000.0$ & $2.0$ & $\mathbf{3433.0}$ & $1000.0$ & $3.0$ & $3766.0$ & $1000.0$ & $4.0$ & $3732.0$ & $1000.0$ & $5.0$ & $4079.0$ & $241.5$ & $2.0$\\[1cm]

		{\LARGE TA55} & $3599.0$ & $1000.0$ & $1.0$ & $\mathbf{3439.0}$  & $1000.0$ & $2.0$ & $3745.0$ & $1000.0$ & $3.0$ & $3878.0$ & $1000.0$ & $4.0$ & $4046.0$ & $1000.0$ & $5.0$ & $4336.0$ & $424.2$ & $4.0$\\	[1cm]

		{\LARGE TA56} & $\mathbf{3465.0}$ & $1000.0$ & $1.0$ & $3471.0$ & $1000.0$ & $2.0$ & $3583.0$ & $1000.0$ & $3.0$ & $4117.0$ & $1000.0$ & $4.0$ & $4069.0$ & $1000.0$ & $5.0$ & $4147.0$ & $212.0$ & $2.0$\\[1cm]

		{\LARGE TA57} & $3695.0$ & $1000.0$ & $1.0$ & $3779.0$ & $1000.0$ & $2.0$ & $\mathbf{3665.0}$ & $1000.0$ & $3.0$ & $4199.0$ & $1000.0$ & $4.0$ & $4096.0$ & $1000.0$ & $5.0$ & $3960.0$ & $208.8$ & $2.0$\\[1cm]

		{\LARGE TA58} & $\mathbf{3642.0}$ & $1000.0$ & $1.0$ & $3777.0$ & $1000.0$ & $2.0$ & $3787.0$ & $1000.0$ & $3.0$ & $3765.0$ & $1000.0$ & $4.0$ & $3826.0$ & $810.3$ & $4.0$ & $4109.0$ & $137.9$ & $1.0$\\[1cm]

		{\LARGE TA59} & $3497.0$ & $1000.0$ & $1.0$ & $\mathbf{3385.0}$ & $1000.0$ & $2.0$ & $3642.0$ & $1000.0$ & $3.0$ & $4032.0$ & $1000.0$ & $4.0$ & $3909.0$ & $1000.0$ & $5.0$ & $4227.0$ & $404.1$ & $3.0$\\[1cm]

		{\LARGE TA60} & $3469.0$ & $1000.0$ & $1.0$ & $\mathbf{3219.0}$ & $1000.0$ & $2.0$ & $3338.0$ & $1000.0$ & $3.0$ & $3426.0$ & $1000.0$ & $4.0$ & $3622.0$ & $1000.0$ & $5.0$ & $3825.0$ & $32.7$ & $0.0$\\ [1cm]
        \hline

		\multirow{3}{*}{{\large AVG}} & \multirow{3}{*}{$3542.1$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$1.0$} & \multirow{3}{*}{$\mathbf{3524.8}$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$2.0$} & \multirow{3}{*}{$3621.5$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$3.0$} & \multirow{3}{*}{$3870.0$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$4.0$} & \multirow{3}{*}{$3908.1$} & \multirow{3}{*}{$978.7$} & \multirow{3}{*}{$4.8$} &  \multirow{3}{*}{$4127.3$} & \multirow{3}{*}{$239.7$} & \multirow{3}{*}{$1.9$}\\ [1cm]

		\hline

	\end{tabular}
    \end{adjustbox}
	}

\end{table}

\begin{table}[ht]
	\fontsize{19pt}{30pt}
	\caption{Results for JSP $50 \times 20$ instances with different TWs} \label{tab: Table02}
	\centering
	%\resizebox{\columnwidth}{!}{%
	\rotatebox{90}{
	\begin{adjustbox}{width=1.7\textwidth}
    \begin{tabular}{|M{2.0cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|}

	%\begin{tabular}{l c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c}
		\hline
		\multirow{3}*{\textbf{{\large Instances}}}  &  \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 01}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 02}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 03}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 04}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 05}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 10}}}} \\[1cm]

		\hline
		& {\large Makespan} & {\Large Timeout}  & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} &  {\large Makespan} & {\Large Timeout} & {\large Interr-calls}\\[1cm]

		{\LARGE TA61} & $3919.0$ & $1000.0$ & $1.0$ & $\mathbf{3537.0}$ & $1000.0$ & $2.0$ & $3604.0$ & $1000.0$ & $3.0$ & $4231.0$ & $1000.0$ & $4.0$ & $4051.0$ & $1000.0$ & $5.0$ & $4463.0$ & $253.0$ & $2.0$\\[1cm]

		{\LARGE TA62} & $3982.0$ & $1000.0$ & $1.0$ & $3610.0$ & $1000.0$ & $2.0$ & $\mathbf{3602.0}$ & $1000.0$ & $3.0$ & $3848.0$ & $1000.0$ & $4.0$ & $3955.0$ & $925.4$ & $4.0$  & $4445.0$ & $326.9$ & $3.0$\\[1cm]

		{\LARGE TA63} & $3746.0$ & $1000.0$ & $1.0$ & $\mathbf{3285.0}$ & $1000.0$ & $2.0$ & $3410.0$ & $1000.0$ & $3.0$ & $3654.0$ & $1000.0$ & $4.0$ & $4295.0$ & $1000.0$ & $5.0$ & $4717.0$ & $311.3$ & $3.0$\\[1cm]

		{\LARGE TA64} & $3610.0$ & $1000.0$ & $1.0$ & $\mathbf{3362.0}$ & $1000.0$ & $2.0$ & $3463.0$ & $1000.0$ & $3.0$ & $3670.0$ & $1000.0$ & $4.0$ & $3929.0$ & $821.3$ & $4.0$ & $4111.0$ & $357.4$ & $2.0$\\[1cm]

		{\LARGE TA65} & $3781.0$ & $1000.0$ & $1.0$ & $\mathbf{3434.0}$ & $1000.0$ & $2.0$ & $3550.0$ & $1000.0$ & $3.0$ & $3639.0$ & $1000.0$ & $4.0$ & $3805.0$ & $1000.0$ & $5.0$ & $4406.0$ & $81.6$ & $0.0$\\	[1cm]

		{\LARGE TA66} & $3895.0$ & $1000.0$ & $1.0$ & $3582.0$ & $1000.0$ & $2.0$ & $\mathbf{3504.0}$ & $1000.0$ & $3.0$ & $4082.0$ & $1000.0$ & $4.0$ & $4077.0$ & $1000.0$ & $5.0$ & $4210.0$ & $249.2$ & $2.0$\\[1cm]

		{\LARGE TA67} & $3866.0$ & $1000.0$ & $1.0$ & $\mathbf{3547.0}$ & $1000.0$ & $2.0$ & $3571.0$ & $1000.0$ & $3.0$ & $4041.0$ & $1000.0$ & $4.0$ & $4115.0$ & $1000.0$ & $5.0$ & $4387.0$ & $285.5$ & $2.0$\\[1cm]

		{\LARGE TA68} & $3763.0$ & $1000.0$ & $1.0$ & $\mathbf{3476.0}$ & $1000.0$ & $2.0$ & $3759.0$ & $1000.0$ & $3.0$ & $3897.0$ & $1000.0$ & $4.0$ & $3855.0$ & $1000.3$ & $5.0$ & $4063.0$ & $210.6$ & $2.0$\\[1cm]

		{\LARGE TA69} & $4121.0$ & $1000.0$ & $1.0$ & $\mathbf{3748.0}$ & $1000.0$ & $2.0$ & $3803.0$ & $1000.0$ & $3.0$ & $4116.0$ & $1000.0$ & $4.0$ & $3937.0$ & $1000.0$ & $5.0$ & $4518.0$ & $111.0$ & $1.0$\\[1cm]

		{\LARGE TA70} & $4111.0$ & $1000.0$ & $1.0$ & $3827.0$ & $1000.0$ & $2.0$ & $\mathbf{3791.0}$ & $1000.0$ & $3.0$ & $4008.0$ & $1000.0$ & $4.0$ & $4044.0$ & $1000.0$ & $5.0$ & $4651.0$ & $365.2$ & $3.0$\\ [1cm]
        \hline

		\multirow{3}{*}{{\LARGE AVG}} & \multirow{3}{*}{$3879.4$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$1.0$} & \multirow{3}{*}{$\mathbf{3540.8}$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$2.0$} & \multirow{3}{*}{$3605.7$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$3.0$} & \multirow{3}{*}{$3918.6$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$4.0$} & \multirow{3}{*}{$4006.3$} & \multirow{3}{*}{$974.3$} & \multirow{3}{*}{$4.8$} & \multirow{3}{*}{$4397.1$} & \multirow{3}{*}{$245.2$} & \multirow{3}{*}{$2.0$}\\ [1cm]

		\hline

	\end{tabular}
    \end{adjustbox}
	}

\end{table}

\begin{table}[ht]
	\fontsize{19pt}{30pt}
	\caption{Results for JSP $100 \times 20$ instances with different TWs} \label{tab: Table03}
	\centering
	%\resizebox{\columnwidth}{!}{%
	\rotatebox{90}{
	\begin{adjustbox}{width=1.7\textwidth}
		%\begin{tabular}[m]{|m{2cm}|*{17}{c}|c|}
    \begin{tabular}{|M{2.0cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|}

        %\begin{tabular}{l c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c}
        \hline
        \multirow{3}*{\textbf{{\large Instances}}}  &  \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 01}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 02}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 03}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 04}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 05}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 10}}}} \\[1cm]

        \hline
        & {\large Makespan} & {\Large Timeout}  & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} &  {\large Makespan} & {\Large Timeout} & {\large Interr-calls}\\[1cm]

		{\LARGE TA71} & $52147.0$ & $1000.0$ & $1.0$ & $21345.0$ & $1000.0$ & $2.0$ & $7641.0$ & $1000.0$ & $3.0$ & $7471.0$ & $1000.0$ & $4.0$ & $\mathbf{7226.0}$ & $1000.0$ & $5.0$ & $8478.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA72} & $45196.0$ & $1000.0$ & $1.0$ & $23505.0$ & $1000.0$ & $2.0$ & $\mathbf{6750.0}$ & $1000.0$ & $3.0$ & $7134.0$ & $1000.0$ & $4.0$ & $7300.0$ & $1000.0$ & $5.0$ & $8164.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA73} & $36548.0$ & $1000.0$ & $1.0$ & $24995.0$ & $1000.0$ & $2.0$ & $7121.0$ & $1000.0$ & $3.0$ & $\mathbf{7027.0}$ & $1000.0$ & $4.0$ & $7416.0$ & $1000.0$ & $5.0$ & $7975.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA74} & $52973.0$ & $1000.0$ & $1.0$ & $25230.0$ & $1000.0$ & $2.0$ & $6703.0$ & $1000.0$ & $3.0$ & $\mathbf{6634.0}$ & $1000.0$ & $4.0$ & $7062.0$ & $1000.0$ & $4.0$ & $7994.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA75} & $45316.0$ & $1000.0$ & $1.0$ & $23651.0$  & $1000.0$ & $2.0$ & $\mathbf{7042.0}$ & $1000.0$ & $3.0$ & $7511.0$ & $1000.0$ & $4.0$ & $7070.0$ & $1000.0$ & $5.0$ & $7934.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA76} & $53532.0$ & $1000.0$ & $1.0$ & $40944.0$ & $1000.0$ & $2.0$ & $7067.0$ & $1000.0$ & $3.0$ & $\mathbf{6879.0}$ & $1000.0$ & $4.0$ & $7061.0$ & $1000.0$ & $5.0$ & $7938.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA77} & $45003.0$ & $1000.0$ & $1.0$ & $24517.0$ & $1000.0$ & $2.0$ & $6947.0$ & $1000.0$ & $3.0$ & $\mathbf{6929.0}$ & $1000.0$ & $4.0$ & $7307.0$ & $1000.0$ & $5.0$ & $7773.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA78} & $41380.0$ & $1000.0$ & $1.0$ & $24686.0$ & $1000.0$ & $2.0$ & $6917.0$ & $1000.0$ & $3.0$ & $\mathbf{6793.0}$ & $1000.0$ & $4.0$ & $7215.0$ & $1000.0$ & $5.0$ & $7986.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA79} & $48827.0$ & $1000.0$ & $1.0$ & $24401.0$ & $1000.0$ & $2.0$ & $6913.0$ & $1000.0$ & $3.0$ & $\mathbf{6621.0}$ & $1000.0$ & $4.0$ & $6645.0$ & $1000.0$ & $5.0$ & $7405.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA80} & $46939.0$ & $1000.0$ & $1.0$ & $22833.0$ & $1000.0$ & $2.0$ & $6925.0$ & $1000.0$ & $3.0$ & $\mathbf{6645.0}$ & $1000.0$ & $4.0$ & $6647.0$ & $1000.0$ & $5.0$ & $7609.0$ & $1000.0$ & $10.0$\\ [1cm]
        \hline

		\multirow{3}{*}{{\LARGE AVG}} & \multirow{3}{*}{$46786.1$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$1.0$} & \multirow{3}{*}{$25610.7$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$2.0$} & \multirow{3}{*}{$7002.6$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$3.0$} & \multirow{3}{*}{$\mathbf{6964.4}$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$4.0$} & \multirow{3}{*}{$7094.9$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$5.0$} & \multirow{3}{*}{$7925.6$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$10.0$}\\ [1cm]

		\hline

	\end{tabular}
    \end{adjustbox}
	}

\end{table}

>>>>

\begin{table}[t]
    \caption{Results for three sizes of job shop scheduling instances with different numbers of time windows using static machine-based EST decomposition \label{tab:Table01}}%
%    \mbox{~}\hfill
%    \resizebox{0.8\textwidth}{!}{%
%    \begin{minipage}{\textwidth}
    \centering
    \begin{tabular}{l l r r r r r}
    \hline
%       & {}        & \multicolumn{6}{c}{Group of Instances}  \\
    Window(s) & Comparison & 50$\times$15 & 50$\times$20 & 100$\times$20 \\

    \hline\\[-2.75mm]
    1                & Makespan             & 3542.1   & 3879.4	     &  46786.1 \\
                     & CPU(Sec)             & 1000.0	& 1000.0   & 1000.0	     	    \\
                     & Interrupted Calls    & 1.0	    & 1.0      & 1.0	       \\[1.5mm]

    2                & Makespan             & 3149.7   & 3479.4	      & 23977.5 \\
                     & CPU(Sec)             & 1000.0	    & 1000.0	   & 1000.0	      \\
                     & Interrupted Calls    & 2.0	    & 2.0      & 2.0	      \\[1.5mm]

    3                & Makespan             & \textbf{3083.8}   & 3290.5	    & 7201.5 \\
                     & CPU(Sec)             & 1000.0	    & 1000.0	   & 1000.0	      \\
                     & Interrupted Calls    & 3.0	    & 3.0      & 3.0	      \\[1.5mm]

    4                & Makespan             & 3110.7   & \textbf{3260.3}	   & 6288.7 \\
                     & CPU(Sec)             & 934.4	    & 944.9	   & 1000.0	      \\
                     & Interrupted Calls    & 3.6	    & 3.5      & 4.0	      \\[1.5mm]

    5                & Makespan             & 3213.6   & 3355.5    & 6106.1 \\
                     & CPU(Sec)             & 615.5	    & 583.4	   & 1000.0	      \\
                     & Interrupted Calls    & 2.7	    & 2.5      & 5.0	      \\[1.5mm]

    6                & Makespan             & 3225.3   & 3414.8	      & \textbf{6031.9} \\
                     & CPU(Sec)             & 243.8	    & 321.5	   & 1000.0	      \\
                     & Interrupted Calls    & 1.0	    & 1.6      & 6.0	      \\[1.5mm]

    7                & Makespan             & 3350.5   & 3540.3	      & 6094.1 \\
                     & CPU(Sec)             & 146.7	    & 161.4	   & 1000.0	      \\
                     & Interrupted Calls    & 0.6	    & 0.9      & 7.0	      \\[1.5mm]

    8                & Makespan             & 3378.5   & 3561.5	      & 6053.1 \\
                     & CPU(Sec)             & 81.0	    & 54.9	   & 1000.0	      \\
                     & Interrupted Calls    & 0.3	    & 0.2      & 8.0	      \\[1.5mm]

    9                & Makespan             & 3495.0   & 3720.7	      & 6095.9 \\
                     & CPU(Sec)             & 45.6	    & 38.0	   & 977.0	      \\
                     & Interrupted Calls    & 0.1	    & 0.2      & 8.2	      \\[1.5mm]

    10               & Makespan             & 3524.9   & 3793.1	      & 6234.0 \\
                     & CPU(Sec)             & 18.5	    & 33.3	   & 861.8	      \\
                     & Interrupted Calls    & 0.1	    & 0.1      & 7.9	      \\[1.5mm]

    \\[-2.75mm]
    \hline
    \end{tabular}
   % }
%    \end{minipage}
% }
%    \hfill\hfill\mbox{~}
\end{table}

\begin{table}[t]
    \caption{Comparing different static/dynamic decomposition strategies \label{tab:Table02}}%
%    \mbox{~}\hfill
%    \resizebox{0.8\textwidth}{!}{%
%    \begin{minipage}{\textwidth}
    \centering
    \begin{tabular}{c c c c c c c c c c}
    \hline

\multirow{2}*{Strategy} & \multicolumn{3}{c}{50$\times$15} & \multicolumn{3}{c}{50$\times$20} & \multicolumn{3}{c}{100$\times$20}\\
    & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC \\
    \hline\\[-2.75mm]
    Static machine-based EST              & \boldmath{$3083.8$}  & $1000.0$   & $3.0$	& \boldmath{$3260.3$}      & $944.9$ & $3.5$ & \boldmath{$6031.9$} & $1000.0$ & $6.0$\\
    [1.5mm]

    Static time-based EST             & $3524.8$ & $1000.0$   & $2.0$	   & $3540.8$      & $1000.0$ & $2.0$ & $6964.4$ & $1000.0$ & $4.0$\\ 
    [1.5mm]

    Static time-based MTWR             & $3456.2$  & $1000.0$   & $2.0$	& $3561.0$      & $1000.0$ & $2.0$ & $7149.6$ & $1000.0$ & $4.0$\\ 
    [1.5mm]

    Dynamic machine-based EST             & $3098.4$  & $1000.0$   & $3.0$	& $3309.5$     & $1000.0$ & $3.3$ & $6115.1$ & $1000.0$ & $6.9$\\ 
    [1.5mm]

    \\[-2.75mm]
    \hline

    \end{tabular}
   % }
%    \end{minipage}
% }
%    \hfill\hfill\mbox{~}
\end{table}

\begin{table}[t]
    \caption{Comparing results of best decomposition strategy with/without dompression and overlapping \label{tab:Table03}}%
%    \mbox{~}\hfill
%    \resizebox{0.8\textwidth}{!}{%
%    \begin{minipage}{\textwidth}
    \centering
    \begin{tabular}{c c c c c c c c c c}

    \hline
    \multicolumn{10}{c}{\textbf{Without Compressing Time Windows}}\\        
\multirow{2}*{Overlap} & \multicolumn{3}{c}{50$\times$15} & \multicolumn{3}{c}{50$\times$20} & \multicolumn{3}{c}{100$\times$20}\\
    & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC \\
    \hline\\[-2.75mm]
    0\%              & $3083.8$  & $1000.0$   & $3.0$	& $3260.3$      & $944.9$ & $3.5$ & $6031.9$ & $1000.0$ & $6.0$\\
    [1.5mm]

    10\%             & $3050.0$  & $1000.0$   & $3.0$	& \boldmath{$3194.9$}     & $1000.0$ & $4.0$ & $5979.9$ & $1000.0$ & $6.0$\\

    20\%             & \boldmath{$3046.0$} & $1000.0$   & $3.0$	   & $3200.6$      & $1000.0$ & $4.0$ & \boldmath{$5954.3$} & $1000.0$ & $6.0$\\

    30\%             & $3051.2$  & $1000.0$   & $3.0$	& $3451.8$      & $1000.0$ & $4.0$ & $6933.3$ & $1000.0$ & $6.0$\\ 
                     [1.5mm]

    \\[-2.75mm]

    \multicolumn{10}{c}{\textbf{Compressing Time Windows}}\\
    \hline
    \multirow{2}*{Overlap} & \multicolumn{3}{c}{50$\times$15} & \multicolumn{3}{c}{50$\times$20} & \multicolumn{3}{c}{100$\times$20}\\
    & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC & Makespan & CPU(Sec) & IC \\
    \hline\\[-2.75mm]
    0\%              & $3013.3$  & $572.3$   & $3.7$	   & $3186.8$      & $540.8$ & $3.3$ & $5713.0$ & $589.2$ & $8.6$\\
    [1.5mm]

    10\%             & $2970.2$  & $600.0$   & $4.0$	   & $3149.8$      & $600.0$ & $4.0$ & $5656.0$ & $600.0$ & $9.0$\\

    20\%             & $2952.2$  & $600.0$   & $4.0$	   & \boldmath{$3147.7$}      & $600.0$ & $4.0$ & \boldmath{$5619.2$} & $600.0$ & $9.0$\\

    30\%             & \boldmath{$2943.1$}  & $600.0$   & $4.0$	   & $3162.2$      & $600.0$ & $4.0$ & $5857.0$ & $600.0$ & $9.0$\\ 
                     [1.5mm]
    \hline
    \end{tabular}
   % }
%    \end{minipage}
% }
%    \hfill\hfill\mbox{~}
\end{table}
